Detecting AI-Generated Images using ResNet

### 2022-12-13 paper/paper.tex
Update paper

Stable Diffusion is originally trained to be a text-to-image model, which means it takes texts as input to describe the images for the model to generate. In order for us to use it as an image-to-image model, we use a pipeline that is similar but swaps the text encoder with the image encoder from CLIP. Since the goal for training CLIP is to maximize the cosine similarities for the image presentation by the image encoder and the text presentation by the text encoder for matching (image, text) pairs, after the CLIP has been trained, the output presentation (vector) from it for matching text and image is very similar, thus the swapped-in image encoder in the Stable Diffusion model we use would play the same role of guiding the diffusion model to generate images similar to the input images. The image encoder from CLIP is used to encode the image into a vector, which is then used as image embedding into the diffusion model to guide it during denoising steps, similar to DALL·E 2's image variation generation API. This way, the model appears to generate variations of the given image that are similar to the them.

>>>>

Stable Diffusion is originally trained to be a text-to-image model, which means it takes texts as input to describe the images for the model to generate. In order for us to use it as an image-to-image model, we use a pipeline that is similar but swaps the text encoder with the image encoder from CLIP. Since the goal for training CLIP is to maximize the cosine similarities for the image presentation by the image encoder and the text presentation by the text encoder for matching (image, text) pairs, after the CLIP has been trained, the output presentations (vectors) from it for matching text and image are very similar, thus the swapped-in image encoder in the Stable Diffusion model we use could play the same role of guiding the diffusion model to generate images similar to the input images. The image encoder from CLIP is used to encode the image into a vector, which is then used as image embedding into the diffusion model to guide it during denoising steps, similar to DALL·E 2's image variation generation API. This way, the model appears to generate variations of the given image that are similar to the them.
